Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-24 man/figures/browning.Rmd
fix sizes

```{r plot}
per_pixels_green <- df %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + 
  geom_bar(stat = 'identity', position = "dodge") + 
  geom_text(aes(label = paste0(per, " %")), position=position_dodge(width=0.9), hjust=-.1, size=2, angle = 90) + 
  facet_wrap(~clu_pop2) + 
  theme_bw() + xlab('') + ylab('Frequency of pixels (%)') +
  theme(strip.background = element_rect(colour = "white", fill = "white"),
        strip.text = element_text(size = 8), 
        axis.title.y = element_text(size = 10, face = 'bold'),
        axis.text = element_text(size = 8),
        panel.grid = element_blank(),
        legend.position = 'bottom') + 
  labs(fill = 'Drought event') + 
  scale_fill_colorblind() + 
  scale_y_continuous(limits = c(0, 110), breaks = c(0, 25, 50, 75, 100))
```

>>>>

```{r plot}
per_pixels_green <- df %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + 
  geom_bar(stat = 'identity', position = "dodge") + 
  geom_text(aes(label = paste0(per, " %")), position=position_dodge(width=0.9), hjust=-.1, size=2, angle = 90) + 
  facet_wrap(~clu_pop2) + 
  theme_bw() + xlab('') + ylab('Frequency of pixels (%)') +
  theme(strip.background = element_rect(colour = "white", fill = "white"),
        strip.text = element_text(size = 7), 
        axis.title.y = element_text(size = 7, face = 'bold'),
        axis.text = element_text(size = 7),
        panel.grid = element_blank(),
        legend.position = 'bottom', 
        legend.text = element_text(size = 7), 
        legend.box.spacing = unit(0.01, "cm"))+
  labs(fill = 'Drought event') + 
  scale_fill_colorblind() + 
  scale_y_continuous(limits = c(0, 110), breaks = c(0, 25, 50, 75, 100)) +
  guides(fill = guide_legend(title.theme = element_text(size = 7)))
```

### 2018-11-24 man/figures/std_anomalies.Rmd
fix sizes

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  ylab(myylab) + xlab('') +
  theme_bw() +
  theme(text = element_text(size=12),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = -0.05, size = 12, 
                                    margin = margin(t=-5, b=1)))
```

>>>>

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_hline(yintercept = 0, size=0.3, colour = "gray") + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  ylab(myylab) + xlab('Year') +
  theme_bw() +
  theme(axis.text = element_text(size=8),
        legend.position = "none",
        panel.grid = element_blank(),
        strip.background = element_rect(fill = "transparent", colour = "black", size = 0.2),
        plot.title = element_text(hjust = -0.05, size = 9, 
                                    margin = margin(t=-5, b=1)))
```
